Analysis of 2005--2015 Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2016-08-16 methodology.tex
improved figure 1

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/pdf/Figure01} 
	\caption{Sketch of the VG method. The initial events of Kopeh Dagh region are represented. Couple of events were deleted due to illustration purposes. The blue vertical lines indicate the events. Height of each line is corresponding the magnitude of the event. The green dashed lines show the allowable connections between events. The connectivity degree (K) of each event is presented. The red arrows show the time difference between events. The $T_c$ and $< T_c >$ values of the last event are represented. Note that the mean of all $<T_c>$ values in each window will be the window mean interval connectivity time.}
	\label{fig:vg}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-01} 
	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh Dagh. The events are identified by vertical thick lines (or sticks) on the horizontal time axis with size equal to the magnitude as indicated by the labels at the bottom of each stick. These sticks are considered to be the obstacles in the time-magnitude space where the graph resides. The visibility graph is composed by the nodes, represented with circles at the tip of each event stick, and the edges or links connecting them. The values inside each node correspond to the connectivity degree, $k$. This value indicates the number straight lines that can be draw between two (mutually visible) nodes without intersecting any obstacle (event stick). The values and time ranges shown at the top correspond to the time difference between events visible by the last event. These times are given in minutes and correspond to individual $T_c$ values. The mean <$T_c^e$> value associated with this event is also shown at the top right. The mean value of all <$T_c^e$> for the events in the graph is the window mean interval connectivity time, <$T_c^e$>.}
	\label{fig:vg}
\end{figure*}
